Title of the document here

### 2015-01-23 rmtw/assignment_1/assignment_1.tex
Added sources
Finished draft of introduction

1. Statement of the problem
  Measuring the inherent readability of various programming languages. 
2. Existing literature
  No previous studies have compared the readability of different programming languages. There are however existing papers that explore the concept of readability. \cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability. \cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system. \cite{hansen2013makes} focus on what makes code hard to read and presents those factors. 
3. Why is it important? 
1, 4 and 8

Industry: To compare code of different language to be able to prioritize them. 
Academia: To conduct more studies on the area which compare different languages.

@@

\nocite{ex1,ex2}
\bibliographystyle{assignment_1}
\bibliography{assignment_1}

>>>>

1. Statement of the problem
  Measuring the inherent readability of various programming languages. 
  \newline \newline
2. Existing literature
  No previous studies have compared the readability of different programming languages. There are however existing papers that explore the concept of readability. \cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability. \cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system. \cite{hansen2013makes} focus on what makes code hard to read and presents those factors. 
  \newline \newline
3. Why is it important?
\cite{aggarwal2002integrated} talks about code maintainability and mentions readability as a factor related to maintainability.

\cite{elshoff1982improving} also talks about readability and how it impacts maintainability. \cite{elshoff1982improving} brings up specific coding standards/conventions/practices to show differences in readability.

\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).

@@

\bibliographystyle{assignment_1}
\bibliography{assignment_1}
